# 서론 {#intro}

서론에는 다음과 같은 내용을 포함한다.
(1) 프로젝트의 목적과 배경을 하나 또는 두개의 문단에 설명
(2) 전체 리포트가 어떤 챕터들을 포함하는지 그리고 각 챕터에서는 어떤 내용을 포함하는 지 간략히 설명

(아래의 내용은 R Markdown으로 사용 가능한 레이블, 인용, R Code Chunks, 테이블 등을 어떻게 사용하는 지 보여줌.)

------

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
